
Construct a data frame with the content you want to merge into your email:

```{r input-data}
dat <-  data.frame(
  email      = c("friend@example.com", "foe@example.com"),
  first_name = c("friend", "foe"),
  thing      = c("something good", "something bad"),
  stringsAsFactors = FALSE
)

```

Write the text of your email as a R markdown document. You can add the subject line in the yaml header.  Use `{}` braces inside the email to refer to the data inside your data frame.  Expressions inside these braces will be encoded by the `glue::glue_data()` function (See https://glue.tidyverse.org/).

```{r markdown-message}
msg <- '
---
subject: "**Hello, {first_name}**"
---

Hi, **{first_name}**

I am writing to tell you about **{thing}**.

{if (first_name == "friend") "Regards" else ""}


Me
'
```

Then you can use `mail_merge()` to embed the content of your data frame into the email message.  By default the email will be shown in a preview window (in the RStudio viewer pane, if you use RStudio).

To send the message, use `send = "draft"` (to save in your gmail drafts folder) or `send = "immediately"` to send the mail immediately.



```{r library}

library(mailmerge)
library(gmailr, quietly = TRUE, warn.conflicts = FALSE)
```

```{r mail-merge}
dat %>% 
  mail_merge(msg)

if (interactive()) {
  dat %>%
    mail_merge(msg) %>%
    print()
}
```

